%%% Template originaly created by Karol Kozioł (mail@karol-koziol.net) and modified for ShareLaTeX use

\documentclass[a4paper,11pt]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{xcolor}

\usepackage{tgtermes}

\usepackage[
pdftitle={Math Assignment}, 
pdfauthor={Zi Wang, New York University},
colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue,bookmarks=true,
bookmarksopenlevel=2]{hyperref}
\usepackage{amsmath,amssymb,amsthm,textcomp}
\usepackage{enumerate}
\usepackage{multicol}
\usepackage{tikz}

\usepackage{geometry}
\geometry{total={210mm,297mm},
left=25mm,right=25mm,%
bindingoffset=0mm, top=20mm,bottom=20mm}


\linespread{1.3}

\newcommand{\linia}{\rule{\linewidth}{0.5pt}}

% custom theorems if needed
\newtheoremstyle{mytheor}
    {1ex}{1ex}{\normalfont}{0pt}{\scshape}{.}{1ex}
    {{\thmname{#1 }}{\thmnumber{#2}}{\thmnote{ (#3)}}}

\theoremstyle{mytheor}
\newtheorem{Proof}{proofnition}

\theoremstyle{mytheor}
\newtheorem{solu}{Solution}

% my own titles
\makeatletter
\renewcommand{\maketitle}{
\begin{center}
\vspace{2ex}
{\huge \textsc{\@title}}
\vspace{1ex}
\\
\linia\\
\@author \hfill \@date
\vspace{4ex}
\end{center}
}
\makeatother
%%%

% custom footers and headers
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{}
\lfoot{Assignment \textnumero{} 3}
\cfoot{}
\rfoot{Page \thepage\ /\ \pageref*{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%

%%%----------%%%----------%%%----------%%%----------%%%

\begin{document}

\title{Assigment 3}

\author{Zi Wang}

\date{04/13/2015}

\maketitle

\section{Problem 2}
To run jacobi and Red-Black Gauss Seidel, you have to provide two arguments. The first one is the sizeo of stencile and the second one is the number of iterations. On this report, we assume the two arguments are 10000, 200000.

Below are some results of Jacobi running on Stampede: TN is the number of threads, T is the time consumed.

TN = 2, T $\approx$ 4.11;

TN = 4, T $\approx$ 2.36;

TN = 8, T $\approx$ 1.54;

TN = 12, T $\approx$ 1.30;

TN = 16, T $\approx$ 5.11;

TN = 20, T $\approx$ 2.60;

TN = 32, T $\approx$ 3.66;


Here are the result of Red-Black Gauss Seidel running on Stampede.

TN = 2, T $\approx$ 4.44;

TN = 4, T $\approx$ 2.74;

TN = 8, T $\approx$ 2.09;

TN = 12, T $\approx$ 2.10;

TN = 16, T $\approx$ 8.41;

TN = 20, T $\approx$ 3.85;

TN = 32, T $\approx$ 6.96;

First, we could observe that Jacobian method is faster than red black Gauss Seidel method. Also, we can see that before 16 threads, the time decreases as the number of threads increases. However, when the number of threads equal 16, the time consumed reaches a peak and then decreases rapidly when TN = 20 and then the time consumption increases when TN = 32. This might be due to communication cost.

\end{document}
